Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-08-17 tables/estimatedparameters.tex
Cleanup table formating

%!TEX root = ../nir_companions.tex
\begin{table*}
  % 
        \small
        \centering
       \begin{threeparttable}[b]
        \caption{Estimated flux ratios, orbital semi-amplitude and RV separation of the companion, given the companion mass (\(\textrm{M}_{2}\) or \(\textrm{M}_{2} \sin{i}\)) from Table~\ref{tab:orbitparams} and observation times from Table~\ref{tab:observations}.} 
        \begin{tabular}{l c c c c c c c c c c}%[hb]
            \toprule
            & Host& Companion & Estimated & Estimated & Estimated & Estimated & & \\  % 2017
            Companion & M$_{K}$ & M$_{K}$ & \(\rm F_{2}/F_{1} \) & \(\rm N_{2}/N_{1} \) (noise ratio) & \(\rm K_2\) & \(\Delta RV\) & Phase coverage\\
            & & & \textit{K}-band & & (\kmps{}) & (\,ms\(^{-1}\)) & (\%)\\
            \midrule
            {HD 4747} & 3.82 & 14.17 & \(7\times10^{-5} \) & 76 & -10.65 & -- & --\\  % 2017
            {HD 162020} & 4.10 & 23.36 & \(2\times10^{-8} \) & 1615 & -98.92\tnote{a} & 2344.24 & 0.28\\  %
            {HD 167665} & 2.60 & 13.21 & \(6\times10^{-5} \) & 105 & -14.47\tnote{a} & 138.45 & 0.18\\  %  -- \(2\times10^{-5} \)  best case based on age rage.
            {HD 168443b} & 2.35 & 42.19 & \(1\times10^{-16} \) & \(1\times10^{8} \) & -64.65\tnote{a}& 257.16 & 0.035\\ 
            {HD 168443c} & 2.35 & 29.55 & \(1\times10^{-11} \) & \(4\times10^{5} \) & -18.05\tnote{a} & 0.95 & 0.001\\  %(c)
            {HD 202206}B & 3.04& 21.63 & \(4\times10^{-8} \) & 1586 & -6.79 & 145.17 & 0.74\\  %(B)   % May2017
            {HD 202206}c & 3.04& 45.63 & \(9\times10^{-18}\) & \(2\times10^{7} \) & -2.50 & 0.67 & 0.15\\  %(B)   % May2017
            {HD 211847}B & 3.50 & 8.40 & 0.011 & 14 & $-$1.85 & 3.88 & 0.09\\  %B % 2017
            {HD 30501} & 3.96 & 10.38 & 0.003 & 27 & -16.12 & 1346.46 & 5.8\\
            \bottomrule& & 
            \end{tabular}
            \label{tab:estimatedparameters}
    \begin{tablenotes}
        \item[a] {Maximum \(K_2\) only given \(M_2 \sin{i}\)}
      \end{tablenotes}
  \end{threeparttable}

\end{table*}

>>>>

%!TEX root = ../nir_companions.tex
\begin{table*}
    \small
    \centering
    \begin{threeparttable}[b]
        \caption{Estimated flux ratios, orbital semi-amplitude and RV separation of the companion, given the companion mass (\(\textrm{M}_{2}\) or \(\textrm{M}_{2} \sin{i}\)) from Table~\ref{tab:orbitparams} and observation times from Table~\ref{tab:observations}.}
        \begin{tabular}{l c c c c c c c c c c}%[hb]
            \toprule
            & Host & Companion & Estimated & Estimated & Estimated & Estimated & & \\  % 2017
            Companion & M$_{K}$ & M$_{K}$ & \(\rm F_{2}/F_{1} \) & \(\rm N_{2}/N_{1} \) (noise ratio) & \(\rm K_2\) & \(\Delta RV\) & Phase coverage\\
            & (mag) & (mag)& \textit{K}-band & & (\kmps{}) & (\,ms\(^{-1}\)) & (\%)\\
            \midrule
            {HD 4747} & 3.82 & 14.17 & \(7\times10^{-5} \) & 76 & -10.65 & -- & --\\  % 2017
            {HD 162020} & 4.10 & 23.36 & \(2\times10^{-8} \) & 1615 & -98.92\tnote{a} & 2344.24 & 0.28\\  %
            {HD 167665} & 2.60 & 13.21 & \(6\times10^{-5} \) & 105 & -14.47\tnote{a} & 138.45 & 0.18\\  %  -- \(2\times10^{-5} \)  best case based on age rage.
            {HD 168443b} & 2.35 & 42.19 & \(1\times10^{-16} \) & \(1\times10^{8} \) & -64.65\tnote{a}& 257.16 & 0.035\\
            {HD 168443c} & 2.35 & 29.55 & \(1\times10^{-11} \) & \(4\times10^{5} \) & -18.05\tnote{a} & 0.95 & 0.001\\  %(c)
            {HD 202206}B & 3.04& 21.63 & \(4\times10^{-8} \) & 1586 & -6.79 & 145.17 & 0.74\\  %(B)   % May2017
            {HD 202206}c & 3.04& 45.63 & \(9\times10^{-18}\) & \(2\times10^{7} \) & -2.50 & 0.67 & 0.15\\  %(B)   % May2017
            {HD 211847}B & 3.50 & 8.40 & 0.011 & 14 & $-$1.85 & 3.88 & 0.09\\  %B % 2017
            {HD 30501} & 3.96 & 10.38 & 0.003 & 27 & -16.12 & 1346.46 & 5.8\\
            \bottomrule& &
            \end{tabular} \label{tab:estimatedparameters}
        \begin{tablenotes}
            \item[a] {Maximum \(K_2\) only given \(M_2 \sin{i}\)}
        \end{tablenotes}
    \end{threeparttable}
\end{table*}

### 2018-08-17 tables/linedepths.tex
Remove threeparttable (for now)
Cleanup table formating

%!TEX root = ../nir_companions.tex

\begin{table}
        \small
    \begin{threeparttable}[b]

   \caption{Contribution of synthetic lines within 2110--2160~nm of synthetic PHOENIX-ACES spectra to a binary model. \(F_{2}/F_{1}\) is the continuum flux ratio between a spectrum with the given \(T_{\textrm{eff}}\) and logg and a Sun-like spectrum with \(T_{\textrm{eff}}=5800\), logg = 4.5 (right most column). \emph{No.\ lines} is the number of spectral lines deeper than 5\% from the continuum of the individual spectra while \emph{avg.\ depth} is the mean depth of those lines. \emph{Cont.\ depth} is the average contribution, or depth, of these lines in the combined spectrum of a binary with a Sun-like spectrum. The SNR is signal-to-noise level required to have Gaussian noise \(\sigma\) =1/SNR equal to the \emph{cont.\ depth} level in the binary model. All synthetic spectra used here have [Fe/H]=0.0.}

    \begin{tabular}{*7c}
        \toprule
        \(T_{\textrm{eff}}\) (K)  & \multicolumn{2}{c}{2300} & \multicolumn{2}{c}{3200} & 5800 (\(\rm F_1\))\\
        logg & 5.0 & 4.5  & 5.0 & 4.5 & 4.5 \\
        \midrule
        \(F_2/F_1\) & 0.006 & 0.019 & 0.029  & 0.091 & 1.000 \\  
        % {>2\%}  & no. lines & 470 &  463 & 414  & 444 & 111 \\
        % & avg.\ depth & 0.20 & 0.23 & 0.10  & 0.12 & 0.04 \\
        % & cont. depth \tablefootmark{a} & 0.0012 &  0.0043 & 0.0028 &  0.0100 &  0.0333\tablefootmark{b} \\ 
        % \midrule
        no.\ lines & 464 & 463 & 365  & 413 & 31 \\
        avg.\ depth & 0.2  & 0.23& 0.11 & 0.12 & 0.10 \\
        cont.\ depth\tnote{a} &  0.0012 & 0.0043 &  0.0031 & 0.0100&  0.0833\tnote{b} \\ 
        SNR  & 833 & 232 & 323  & 100 & 12 \\ 
        %  SNR\(\rm _N\)  & 39 & 11 & 17  & 5 & 2 \\ 
        \bottomrule
    \end{tabular}
    \begin{tablenotes}
        \item [a] avg.\ depth \(\times~ \rm F_2 / (F_1 + F_2)\), where \(F_1\) is the component in the far right column.
        \item[b] avg.\ depth \(\times~ \rm F_1 / (F_1 + F_2)\), where \(\rm F_2\) is for the companion with \(T_{\textrm{eff}}\)=3200, logg=4.5.
    \end{tablenotes}
    \end{threeparttable}
    \label{tab:line_contributions}
\end{table}

>>>>

%!TEX root = ../nir_companions.tex
\begin{table}
    \small
    \centering
    \begin{threeparttable}[b]

   \caption{Contribution of synthetic lines within 2110--2160~nm of synthetic PHOENIX-ACES spectra to a binary model. \(F_{2}/F_{1}\) is the continuum flux ratio between a spectrum with the given \(T_{\textrm{eff}}\) and logg and a Sun-like spectrum with \(T_{\textrm{eff}}=5800\), logg = 4.5 (right most column). \emph{No.\ lines} is the number of spectral lines deeper than 5 per cent from the continuum of the individual spectra while \emph{avg.\ depth} is the mean depth of those lines. \emph{Cont.\ depth} is the average contribution, or depth, of these lines in the combined spectrum of a binary with a Sun-like spectrum. The SNR is signal-to-noise level required to have Gaussian noise \(\sigma\) = 1/SNR equal to the \emph{cont.\ depth} level in the binary model. All synthetic spectra used here have [Fe/H] = 0.0.}

    \begin{tabular}{*7c}
        \toprule
        \(T_{\textrm{eff}}\) (K)  & \multicolumn{2}{c}{2300} & \multicolumn{2}{c}{3200} & 5800 (\(\rm F_1\))\\
        logg & 5.0 & 4.5  & 5.0 & 4.5 & 4.5 \\
        \midrule
        \(F_2/F_1\) & 0.006 & 0.019 & 0.029  & 0.091 & 1.000 \\
        no.\ lines & 464 & 463 & 365  & 413 & 31 \\
        avg.\ depth & 0.2  & 0.23& 0.11 & 0.12 & 0.10 \\
        cont.\ depth\tnote{a} &  0.0012 & 0.0043 &  0.0031 & 0.0100&  0.0833\tnote{b} \\
        SNR  & 833 & 232 & 323  & 100 & 12 \\
        \bottomrule
    \end{tabular}\label{tab:line_contributions}
    \begin{tablenotes}
        \item [a] avg.\ depth \(\times~ \rm F_2 / (F_1 + F_2)\), where \(F_1\) is the component in the far right column.
        \item[b] avg.\ depth \(\times~ \rm F_1 / (F_1 + F_2)\), where \(\rm F_2\) is for the companion with \(T_{\textrm{eff}}\) = 3200, logg = 4.5.
    \end{tablenotes}
  \end{threeparttable}
\end{table}

### 2018-08-17 tables/observation_table.tex
Cleanup table formating

% Table of observations
\begin{table*}
    \small
            \centering  
           \begin{threeparttable}[b]

            \caption{Details about the each CRIRES observation. {\rd The time, settings, number of artefacts removed, the SNR obtained and the predicted orbital state of each system are provided.}}
            %\begin{tabular}{l c c c c cl cl r@{.}l r@{.}l r@{.}l}
            \begin{tabular}{l c c c c c c r@{.}l r@{.}l r@{.}l}
                \toprule
                Object & Obs. \# & Start date  & Filter & Airmass  & Artefacts & SNR & \multicolumn{2}{c}{\(RV_1\)} & \multicolumn{2}{c}{\(RV_2\)} & \multicolumn{2}{c}{\(rv_2\)}  \\  % & \(Date \)
                &   & (yyyy-mm-dd hh:mm:ss)  &  & (at start) & {\rd/ 32} & & \multicolumn{2}{c}{kms\(^{-1}\)} & \multicolumn{2}{c}{kms\(^{-1}\)} & \multicolumn{2}{c}{kms\(^{-1}\)}\\ % data ref    % & (JD\(^{\star} \))
                \midrule
                {HD 4747}   & 1 & 2012-07-06 07:36:06 & Ks     	      & 1.25  	  & 7 & 340 & $-$0    & 219 & $-$0  & 154 & 0&065 \\ %-1      & 2456114.81674
                {HD 162020} & 1 & 2012-07-04 06:23:22 & Ks     		& 1.30 		& 2 & 127 & $-$28  & 760 & 50 & 785\tnote{a}  & 79&545\tnote{a} \\ %-1      & 2456112.76624
                {HD 162020} & 2 & 2012-07-04 06:57:48 & Ks     		& 1.44  	& 2 & 128 & $-$28  & 717 & 48 & 440\tnote{a} & 77&157\tnote{a} \\ %-2      & 2456112.79015
                {HD 167665} & 1 & 2012-07-28 05:00:53 & Hx5e-2 	& 1.24 		& 7 & 371 & 7         & 581 & 18 & 024\tnote{a} & 10&443\tnote{a} \\ %-1a     & 2456136.70895
                {HD 167665} & 2 & 2012-07-28 05:37:27 & Hx5e-2 	& 1.39  	& 4 & 374 & 7         & 581 & 18 & 025\tnote{a}  & 10&444\tnote{a} \\ %-1b     & 2456136.73434
                {HD 167665} & 3 & 2012-08-05 02:54:03 & Hx5e-2 	& 1.04  	& 4 & 358 & 7         & 575 & 18 & 163\tnote{a} & 10&588\tnote{a} \\ %-2      & 2456144.62087
                {HD 168443} & 1 & 2012-08-05 04:29:32 & Ks     		& 1.31 		& 2& 192 & $-$0   & 121 & 50 & 932\tnote{a,b}  & 51&053\tnote{a,b} \\ %-1      & 2456144.68718
                {HD 168443} & 2 & 2012-08-05 04:58:50 & Ks     		& 1.47 		& 4 & 190 & $-$0   & 121 & 51 & 189 \tnote{a,b} & 51&310\tnote{a,b} \\ %-2      & 2456144.70753
                {HD 202206} & 1 & 2012-07-12 06:54:44 & Ks     		& 1.01 		& 3& 189 & 14      & 843 & 12 & 992\tnote{b}  & -1&851 \\ %-1      & 2456120.78801
                {HD 202206} & 2 & 2012-07-13 05:41:40 & J       	  & 1.01 	  & 3 & 209 & 14      & 837 & 13 & 065\tnote{b}  & -1&772 \\ %-2      & 2456121.73727
                {HD 202206} & 3 & 2012-07-11 08:29:55 & Ks     		& 1.15		& 4& 180 & 14      & 849 & 12 & 920\tnote{b}  & -1&929 \\ %-3      & 2456119.85411
                {HD 211847} & 1 & 2012-07-06 07:02:57 & Ks     		& 1.07 		& 4& 272 & 6        & 613 & 7   & 171 & 0& 558\\ %-1      & 2456114.79372
                {HD 211847} & 2 & 2012-07-13 06:54:37 & Ks     		& 1.05 		& 5& 283 & 6        & 614 & 7   & 167 & 0&553 \\ %-2      & 2456121.78793
                {HD 30501}  & 1 & 2012-04-07 00:08:29 & Hx5e-2 	 & 1.60 	 & 3& 217 & 22      &  372 & 36 & 377 & 14&005 \\ %-1      & 2456024.50590
                {HD 30501}  & 2 & 2012-08-01 09:17:30 & Hx5e-2    & 1.42     & 10& 212 & 22      & 505 & 35  & 120 & 12&615 \\ %-2a     & 2456140.88716
                {HD 30501}  & 3 & 2012-08-02 08:47:30 & Hx5e-2 	 & 1.53 	 & 8& 237 & 22      & 507 &  35 & 102 & 12&595 \\ %-3      & 2456141.86633
                {HD 30501}  & 4 & 2012-08-06 09:42:07 & Ks     		 & 1.28 	 & 7& 235& 22      & 514 & 35 & 031 & 12&517 \\ %-2b     & 2456145.90426
                \bottomrule
                & & & & 
        \end{tabular}
        \label{tab:observations}
        \begin{tablenotes}
          \item  [a]{Maximum RV given \(\textrm{M}_2\sin{i}\) only.}
          \item  [b]{Largest mass companion only.}
        \end{tablenotes}
    \end{threeparttable}

\end{table*}

>>>>

% Table of observations
\begin{table*}
    \small
    \centering
    \begin{threeparttable}[b]
        \caption{Details about the each CRIRES observation. {The time, settings, number of artefacts removed, the SNR obtained and the predicted orbital state of each system are provided.}}
        \begin{tabular}{l c c c c c c r@{.}l r@{.}l r@{.}l}
            \toprule
            Object & Obs. \# & Start date  & Filter & Airmass  & Artefacts & SNR & \multicolumn{2}{c}{\(RV_1\)} & \multicolumn{2}{c}{\(RV_2\)} & \multicolumn{2}{c}{\(rv_2\)}  \\  % & \(Date \)
            &   & (yyyy-mm-dd hh:mm:ss)  &  & (at start) & {/ 32} & & \multicolumn{2}{c}{kms\(^{-1}\)} & \multicolumn{2}{c}{kms\(^{-1}\)} & \multicolumn{2}{c}{kms\(^{-1}\)}\\ % data ref    % & (JD\(^{\star} \))
            \midrule
            {HD 4747}   & 1 & 2012-07-06 07:36:06 & Ks     	 & 1.25  	  & 7 & 340 & $-$0    & 219 & $-$0  & 154 & 0&065 \\ %-1      & 2456114.81674
            {HD 162020} & 1 & 2012-07-04 06:23:22 & Ks     		& 1.30 		& 2 & 127 & $-$28  & 760 & 50 & 785\tnote{a}  & 79&545\tnote{a} \\ %-1      & 2456112.76624
            {HD 162020} & 2 & 2012-07-04 06:57:48 & Ks     		& 1.44  	& 2 & 128 & $-$28  & 717 & 48 & 440\tnote{a} & 77&157\tnote{a} \\ %-2      & 2456112.79015
            {HD 167665} & 1 & 2012-07-28 05:00:53 & Hx5e-2 	& 1.24 		& 7 & 371 & 7         & 581 & 18 & 024\tnote{a} & 10&443\tnote{a} \\ %-1a     & 2456136.70895
            {HD 167665} & 2 & 2012-07-28 05:37:27 & Hx5e-2 	& 1.39  	& 4 & 374 & 7         & 581 & 18 & 025\tnote{a} & 10&444\tnote{a} \\ %-1b     & 2456136.73434
            {HD 167665} & 3 & 2012-08-05 02:54:03 & Hx5e-2 	& 1.04  	& 4 & 358 & 7         & 575 & 18 & 163\tnote{a} & 10&588\tnote{a} \\ %-2      & 2456144.62087
            {HD 168443} & 1 & 2012-08-05 04:29:32 & Ks     		& 1.31 		& 2& 192 & $-$0   & 121 & 50 & 932\tnote{a,b}  & 51&053\tnote{a,b} \\ %-1      & 2456144.68718
            {HD 168443} & 2 & 2012-08-05 04:58:50 & Ks     		& 1.47 		& 4 & 190 & $-$0   & 121 & 51 & 189\tnote{a,b} & 51&310\tnote{a,b} \\ %-2      & 2456144.70753
            {HD 202206} & 1 & 2012-07-12 06:54:44 & Ks     		& 1.01 		& 3& 189 & 14      & 843 & 12 & 992\tnote{b}  & -1&851 \\ %-1      & 2456120.78801
            {HD 202206} & 2 & 2012-07-13 05:41:40 & J       	  & 1.01 	  & 3 & 209 & 14      & 837 & 13 & 065\tnote{b}  & -1&772 \\ %-2      & 2456121.73727
            {HD 202206} & 3 & 2012-07-11 08:29:55 & Ks     		& 1.15		& 4& 180 & 14      & 849 & 12 & 920\tnote{b}  & -1&929 \\ %-3      & 2456119.85411
            {HD 211847} & 1 & 2012-07-06 07:02:57 & Ks     		& 1.07 		& 4& 272 & 6        & 613 & 7   & 171 & 0& 558\\ %-1      & 2456114.79372
            {HD 211847} & 2 & 2012-07-13 06:54:37 & Ks     		& 1.05 		& 5& 283 & 6        & 614 & 7   & 167 & 0&553 \\ %-2      & 2456121.78793
            {HD 30501}  & 1 & 2012-04-07 00:08:29 & Hx5e-2 	 & 1.60 	 & 3& 217 & 22      &  372 & 36 & 377 & 14&005 \\ %-1      & 2456024.50590
            {HD 30501}  & 2 & 2012-08-01 09:17:30 & Hx5e-2    & 1.42     & 10& 212 & 22      & 505 & 35  & 120 & 12&615 \\ %-2a     & 2456140.88716
            {HD 30501}  & 3 & 2012-08-02 08:47:30 & Hx5e-2 	 & 1.53 	 & 8& 237 & 22      & 507 &  35 & 102 & 12&595 \\ %-3      & 2456141.86633
            {HD 30501}  & 4 & 2012-08-06 09:42:07 & Ks     		 & 1.28 	 & 7& 235& 22      & 514 & 35 & 031 & 12&517 \\ %-2b     & 2456145.90426
            \bottomrule
        \end{tabular}\label{tab:observations}
        \begin{tablenotes}
          \item  [a]{Maximum RV given \(\textrm{M}_2\sin{i}\) only.}
          \item  [b]{Largest mass companion only.}
        \end{tablenotes}
    \end{threeparttable}
\end{table*}

### 2018-08-17 tables/recoveredparameters.tex
Use threeparttbale and caption
push to get finished
Cleanup table formating

\begin{table*}
    \begin{threeparttable}
    \caption{Input and recovered parameters on simulations and an observation when applying a single (\(\rm C^1\)) and binary (\(\rm C^2\)) models. The logg and metallicity were fixed at \(\rm logg_1 = 4.50\), \(\rm logg_2=5.0\) and [Fe/H]=0.0 equally for both components. Gaussian noise was added to both simulations with a SNR of 150.}
    \centering
    \begin{tabular}{c | *3c | *3c | *3c}
        \toprule
        & \multicolumn{3}{c|}{Simulation 1} & \multicolumn{3}{c|}{Simulation 2} & \multicolumn{3}{c}{Observed {HD 211847}} \\
        \midrule
        & Input & \multicolumn{2}{c|}{Recovered} & Input & \multicolumn{2}{c|}{Recovered} & Expected & \multicolumn{2}{c}{Recovered} \\
        & & \(C^1\) & \(C^2\) & & \(C^1\) & \(C^2\) & & \(C^1\)  & \(C^2\) \\
        \midrule
        \(T_{\textrm{eff}_1}\) & 5800 & 5800 & 5800 & 5700 & 5800 & 5700 & \(5715 \pm 24\) & 5900 & 5800\\
        \(T_{\textrm{eff}_2}\) & 4000 & -- & 3800 & 3200 & -- & 3100 & \(\sim3200\) & -- & >3800\tnote{a}\\
        \({rv}_1\) & 0 & 0.1 & 0 & 6.6 & 6.6 & 6.6 & \(6.6 \pm 0.3\) & 7& 7.6 \\
        \({rv}_2\) &  10 & -- & 9.8 & 0.5 & -- &  -1& \(0.5 \pm 2\) & -- &-12.6\\
        \midrule
        \(R_1/R_2\)& 2.57 & -- & 2.71& 3.16 & - & 3.27 & 3.16 & -- & <2.71\tnote{a}\\
        \(\rm F_2/F_1\)& 0.084 & -- & 0.066 & 0.030 & -- & 0.026 & 0.030 & -- & >0.066\tnote{a}\\
        \(\chi^2\)& -- & 4978 & 3792 & -- & 3746 & 3630  & -- & 37688 & 33860\\
        \(\chi^2_{red}\) & -- & 1.62 & 1.24 & -- & 1.22 & 1.18 & -- & 21.3 & 19.2\\
        \bottomrule
    \end{tabular}
    \begin{tablenotes}
       \item [a] {At the arbitrary upper limit for companion temperature grid (3800~K).}
    \end{tablenotes}
    \end{threeparttable}
    \label{tab:example_params}
\end{table*}

>>>>

\begin{table*}
    \centering
    \begin{threeparttable}
        \caption{Input and recovered parameters on simulations and an observation when applying a single (\(\rm C^1\)) and binary (\(\rm C^2\)) models. The logg and metallicity were fixed at \(\rm logg_1=4.50\), \(\rm logg_2=5.0\) and [Fe/H]=0.0 equally for both components. Gaussian noise was added to both simulations with a SNR of 150. {Here $m$ and $n$ are the number of data points and parameters used in each model.}}
        \begin{tabular}{c | *3c | *3c | *3c}
            \toprule
            & \multicolumn{3}{c|}{Simulation 1} & \multicolumn{3}{c|}{Simulation 2} & \multicolumn{3}{c}{Observed {HD 211847}} \\
            \midrule
            & Input & \multicolumn{2}{c|}{Recovered} & Input & \multicolumn{2}{c|}{Recovered} & Expected & \multicolumn{2}{c}{Recovered} \\
            & & \(C^1\) & \(C^2\) & & \(C^1\) & \(C^2\) & & \(C^1\)  & \(C^2\) \\
            \midrule
            \(T_{\textrm{eff}_1}\) & 5800 & 5800 & 5800 & 5700 & 5800 & 5700 & \(5715 \pm 24\) & 5900 & 5800\\
            \(T_{\textrm{eff}_2}\) & 4000 & -- & 3800 & 3200 & -- & 3100 & \(\sim\)3200 & -- & >3800\tnote{a}\\
            \({rv}_1\) & 0 & 0.1 & 0 & 6.6 & 6.6 & 6.6 & \(6.6 \pm 0.3\) & 7& 7.6 \\
            \({rv}_2\) &  10 & -- & 9.8 & 0.5 & -- &  -1& \(0.5 \pm 2\) & -- &-12.6\\
            \midrule
            \(R_1/R_2\)& 2.57 & -- & 2.71& 3.16 & - & 3.27 & 3.16 & -- & <2.71\tnote{a}\\
            \(\rm F_2/F_1\)& 0.084 & -- & 0.066 & 0.030 & -- & 0.026 & 0.030 & -- & >0.066\tnote{a}\\
            {$m$} & - & 3072 & 3072 & -- & 3072 & 3072 & -- & 2612 & 2612\\
            {$n$} & - & 2 & 4 & -- & 2 & 4 & -- & 2 & 4\\
            \(\chi^2\)& -- & 4978 & 3792 & -- & 3746 & 3630  & -- & 37688 & 33860\\
            \(\chi^2_{red}\) & -- & 1.62 & 1.24 & -- & 1.22 & 1.18 & -- & 21.3 & 19.2\\
            {BIC} & -- & -20145 & -22315 & -- & -21477& -21377& -- & 18281 & 14468\\
            \bottomrule
        \end{tabular}\label{tab:example_params}
        \begin{tablenotes}
           \item [a] {At the arbitrary upper limit for companion temperature grid (3800~K).}
        \end{tablenotes}
    \end{threeparttable}
\end{table*}

### 2018-08-17 tables/stellarparameters.tex
Cleanup table formating

%% Table of stellar parameters
\begin{table*}
        \small
        \centering
        \begin{threeparttable}[b]

        \caption{Stellar parameters of the target companion's host stars. V is the apparent magnitude taken from {SIMBAD}~\citep{wenger_simbad_2000}. {\rd{} Distances were calculated from the GAIA parallax measurements.}}
        \begin{tabular}{l c c r@{$~\pm~$}l r@{$~\pm~$}l r@{$~\pm~$}l r@{$~\pm~$}l c c c}
            \toprule
            Star & SpT & V &  \multicolumn{2}{c}{\(T_{\textrm{eff}}\) (K)} &  \multicolumn{2}{c}{logg (cm s\(^{-2} \))}  & \multicolumn{2}{c}{[Fe/H]} &  \multicolumn{2}{c}{\(M_1\) (\textrm{M}\(_{\sun} \))} & Age (Gyr) & d (pc) & Reference\\
            \midrule
            {HD 4747}     & K0V & 7.15 & 5316 & 50 & 4.48 & 0.10  & $-$0.21 & 0.05 & 0.81 & 0.02  & $3.3 \pm 2.3$   & $18.80 \pm 0.04$ & 1, 2, 3, 8 \\ 
            {HD 162020} & K3V & 9.12 & 4723 & 71 & 4.31 & 0.18  & $-$0.10 & 0.03 & 0.74 & 0.07  & $3.1 \pm 2.7$   & $30.85 \pm 0.06$ & 4, 5, 6, 8 \\  
            {HD 167665} & F9V & 6.40 & 6224 & 50 & 4.44 & 0.10  & 0.05       & 0.06 & 1.14 & 0.03  & 0.7 -- 3.6           & $ 31.24 \pm 0.06$ & 1, 8 \\
            {HD 168443} & G6V & 6.92 & 5617 & 35 & 4.22 & 0.05 & 0.06       & 0.05 & 1.01 & 0.07  & $10.0 \pm 0.3$  & $39.67 \pm 0.12$ & 5, 6, 8 \\ 
            {HD 202206} & G6V & 8.07 & 5757 & 25 & 4.47 & 0.03 & 0.29       & 0.02 & 1.04 & 0.07  & $2.9 \pm 1.0$    & $46.03 \pm 0.14$ & 5, 7, 8 \\ 
            {HD 211847} & G5V & 8.62 & 5715 & 24 & 4.49 & 0.05 & $-$0.08 & 0.02 & 0.92 & 0.07   & 0.1 -- 6.0            & $48.81 \pm 0.13 $ & 1, 2, 4, 8 \\ 
            {HD 30501}   & K2V & 7.59  & 5223 & 50 & 4.56 & 0.10 & 0.06       & 0.06 & 0.81 & 0.02  & 0.8 -- 7.0           & $20.37 \pm 0.01$ & 1, 4, 8 \\
            \bottomrule
        \end{tabular}
         \label{tab:starparams}
        \begin{tablenotes}
           \item[] References: (1)~\citet{sahlmann_search_2011}; (2)~\citet{santos_spectroscopic_2005}; (3)~\citet{crepp_trends_2016}; (4)~\citet{tsantaki_deriving_2013}; (5)~\cite{bonfanti_age_2016}; (6)~\citet{santos_spectroscopic_2004}; (7)~\citet{sousa_spectroscopic_2008}; {\rd(8)}~\citet{collaboration_gaia_2018};
         \end{tablenotes}
       \end{threeparttable}

\end{table*}

>>>>

%% Table of stellar parameters
\begin{table*}
    \small
    \centering
    \begin{threeparttable}[b]
        \caption{Stellar parameters of the target companion's host stars. V is the apparent magnitude taken from {SIMBAD}~\citep{wenger_simbad_2000}. {Distances were calculated from the GAIA parallax measurements.}}
        \begin{tabular}{l c c r@{$~\pm~$}l r@{$~\pm~$}l r@{$~\pm~$}l r@{$~\pm~$}l c c c}
            \toprule
            Star & SpT & V & \multicolumn{2}{c}{\(T_{\textrm{eff}}\) (K)} &  \multicolumn{2}{c}{logg (cm s\(^{-2} \))}  & \multicolumn{2}{c}{[Fe/H]} &  \multicolumn{2}{c}{\(M_1\) (\textrm{M}\(_{\sun} \))} & Age (Gyr) & d (pc) & Reference\\
            \midrule
            {HD 4747}     & K0V & 7.15 & 5316 & 50 & 4.48 & 0.10  & $-$0.21 & 0.05 & 0.81 & 0.02  & $3.3 \pm 2.3$   & $18.80 \pm 0.04$ & 1, 2, 3, 8 \\
            {HD 162020} & K3V & 9.12 & 4723 & 71 & 4.31 & 0.18  & $-$0.10 & 0.03 & 0.74 & 0.07  & $3.1 \pm 2.7$   & $30.85 \pm 0.06$ & 4, 5, 6, 8 \\
            {HD 167665} & F9V & 6.40 & 6224 & 50 & 4.44 & 0.10  & 0.05       & 0.06 & 1.14 & 0.03  & 0.7 -- 3.6           & $ 31.24 \pm 0.06$ & 1, 8 \\
            {HD 168443} & G6V & 6.92 & 5617 & 35 & 4.22 & 0.05 & 0.06       & 0.05 & 1.01 & 0.07  & $10.0 \pm 0.3$  & $39.67 \pm 0.12$ & 5, 6, 8 \\
            {HD 202206} & G6V & 8.07 & 5757 & 25 & 4.47 & 0.03 & 0.29       & 0.02 & 1.04 & 0.07  & $2.9 \pm 1.0$    & $46.03 \pm 0.14$ & 5, 7, 8 \\
            {HD 211847} & G5V & 8.62 & 5715 & 24 & 4.49 & 0.05 & $-$0.08 & 0.02 & 0.92 & 0.07   & 0.1 -- 6.0            & $48.81 \pm 0.13 $ & 1, 2, 4, 8 \\
            {HD 30501}   & K2V & 7.59  & 5223 & 50 & 4.56 & 0.10 & 0.06       & 0.06 & 0.81 & 0.02  & 0.8 -- 7.0           & $20.37 \pm 0.01$ & 1, 4, 8 \\
            \bottomrule
        \end{tabular} \label{tab:starparams}
        \begin{tablenotes}
           \item[] References: (1)~\citet{sahlmann_search_2011}; (2)~\citet{santos_spectroscopic_2005}; (3)~\citet{crepp_trends_2016}; (4)~\citet{tsantaki_deriving_2013}; (5)~\cite{bonfanti_age_2016}; (6)~\citet{santos_spectroscopic_2004}; (7)~\citet{sousa_spectroscopic_2008}; (8)~\citet{collaboration_gaia_2018};
        \end{tablenotes}
    \end{threeparttable}
\end{table*}
